---
title: "PSY 8960 Week 8 Project"
author: "Reed Priest"
date: "`r Sys.Date()`"
output: html_document
df_print: paged
---

**Reproducable Image and Online Resources**

An image of this project as of *`r Sys.Date()`* can be accessed by [clicking this link](X). An interactive web app is available by [clicking this link](https://reedpumn.shinyapps.io/shinyweek8/) instead.

**Script Settings and Resources**

```{r Setting working directory, message = FALSE}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
```

**Data Import and Cleaning**

This section makes the data tidy and prepares them for analysis. Two new variables were calculated to later correlate them.

```{r Data preparation}
week8_tbl <- read_csv("../data/week3.csv") %>%
  rowwise() %>%
  mutate(q5 = 6 - q5,
         q1_6 = mean(c(q1:q6)),
         q8_10 = mean(c(q8:q10)),
         gender = factor(gender, levels = c("M", "F"), labels=c("Male","Female")))
```

**Visualization**

This section shows our dataset and visualizes the linear relationship between the means of questions one through six with the mean of questions eight through ten. I chose to: 1) rename the axes to enable clearer interpretations and 2) jitter the data to prevent overlapped points from obscuring the graph.

```{r Making graph, echo = FALSE}
week8_tbl %>%
  select(q1:q6)

ggplot(week8_tbl, aes(x = q1_6, y = q8_10)) +
  geom_jitter() +
  geom_smooth(method = "lm", se = TRUE, color = "purple") +
  labs(x = "Mean of Questions 1-6", y = "Mean of Questions 8-10")
```

**Analysis**

This section correlated the two means of our main variables.

```{r Correlation calculation}
cor.test(week8_tbl$q1_6, week8_tbl$q8_10)
```

I observed a correlation of `r round(cor.test(week8_tbl$q1_6, week8_tbl$q8_10)[[4]], 2)`. The p-value is not less than .05; therefore, we fail to conclude they have a significant relationship.

**Data Export**

This section exports the relevant columns of our dataset to be used in a skinny format. This is done to communicate our raw data.

```{r Exporting}
week8_tbl %>%
  select(-timeStart, -condition, -q7) %>%
  saveRDS(file = "../shinyweek8/shinydata_tbl.rds")
```
